PeerMind: Towards Collective Decision-Making

### 2016-11-29 paper.tex
Style.

%Using dynamic quorum, score voting, delegation, and nice integration with UI/UX.

@@

Range voting (score voting) is voting where members of a community express their positions on open proposals by assigning
each a score on a fixed scale, in the context of this paper, between $-1$ and $+1$.
Prior work has shown that this approach generalizes many previous approaches to voting and allows members to express their
positions in a highly informative and precise manner.
We find it especially suitable for a web application because many web users are used to use it when ranking products
and giving other ``five-star'' feedback.
Moreover, if later on a new proposal is added to a set of existing proposals on which voting was already open, only the
new proposal needs to be evaluated by members, as opposed to alternative voting systems where the relative rankings of
each proposal would need reassessing (assuming members use a consistent personal scale when voting).

@@

@@

\subsubsection{Problem Statement}
We wish to compute the probability that the bias in a population towards voting ``yes'' is greater than some
fraction of the population (e.g., $50\%$ for a simple majority, $67\%$ for a super majority, $90\%$ for a consensus).
In addition, we wish to compute the probability that the bias towards voting ``yes'' on a specific item is greater
than the bias towards voting ``yes'' on all other competing items.

@@

\subsubsection{Voting}
We allow for score voting where each member of the population may choose any real number in the range $[-1,+1]$ to
represent their vote, with $-1$ representing opposition and $+1$ representing support.
In the theory subsection below, we rescale votes to be in the range $[0,1]$ via the notation $\frac{votes + 1}{2}$.

@@

\subsubsection{Bayesian Theory}
To properly understand the Bayesian approach to parameter estimation, read the following instructive tutorial:
\url{http://www.behind-the-enemy-lines.com/2008/01/are-you-bayesian-or-frequentist-or.html}

The above tutorial is very similar to the problem we have at hand.
The commonplace and convenient choice of using the Beta distribution as our prior on the population bias is a
consequence of the Beta distribution's conjugacy with the binomial distribution, a distribution that arises
naturally when considering samples from a finite population.

After extracting the sufficient statistics from raw votes --- namely the average score and the number of
abstentions --- we can adjust the effective population size and corresponding threshold.
In addition, we can calculate the effective number of ``yes'' and ``no'' votes, which one can think of as the number
of Heads and Tails in the aforementioned tutorial.

@@

To continue with our example, let's say that $M_1$ and $M_3$ voted for a decision with $0.7$ and against with $0.4$,
respectively.
We are using score voting on $[-1, 1]$ range, so those votes are $v_1 = V_1 = 0.7$ and
$v_3 = V_3 = -0.4$.

>>>>

%Using dynamic quorum, range voting, delegation, and nice integration with UI/UX.

@@

Range voting (also known as score voting) is voting where members of a community express their positions on open proposals by assigning
each a score on a fixed scale, in the context of this paper, between $-1$ and $+1$.
A proposal passes if the average score of all votes on a position is positive.
When multiple competing proposals are being voted on, the one with highest average score wins.

Prior work has shown that this approach generalizes many previous approaches to voting and allows members to express their
positions in a highly informative and precise manner.
We find it especially suitable for a web application because many web users are used to use it when ranking products
and giving other ``five-star'' feedback.
Moreover, if later on a new proposal is added to a set of existing proposals on which voting was already open, only the
new proposal needs to be evaluated by members, as opposed to alternative voting systems where the relative rankings of
each proposal would need reassessing (assuming members use a consistent personal scale when voting).

@@

%\todo[inline]{Unify terminology: population -> community, voters -> members, item -> proposal}

@@

\subsubsection{Problem Statement}
We wish to compute the probability that the bias in a population towards voting ``yes'' is greater than some
fraction of the population (e.g., $50\%$ for a simple majority, $67\%$ for a super majority).
In addition, we wish to compute the probability that the bias towards voting ``yes'' on a specific item is greater
than the bias towards voting ``yes'' on all other competing items.

@@

\subsubsection{Voting}
We allow for range voting where each member of the population may choose any real number in the range $[-1,+1]$ to
represent their vote, with $-1$ representing opposition and $+1$ representing support.
In the theory subsection below, we rescale votes to be in the range $[0,1]$ via the notation $\frac{votes + 1}{2}$.

@@

\subsubsection{Bayesian Theory}

The commonplace and convenient choice of using the Beta distribution as our prior on the population bias is a
consequence of the Beta distribution's conjugacy with the binomial distribution, a distribution that arises
naturally when considering samples from a finite population.\footnote{To
properly understand the Bayesian approach to parameter estimation, read the following instructive tutorial:
\url{http://www.behind-the-enemy-lines.com/2008/01/are-you-bayesian-or-frequentist-or.html}
The tutorial is very similar to the problem we have at hand.}

After extracting the sufficient statistics from raw votes~---~namely the average score and the number of
abstentions~---~we can adjust the effective population size and corresponding threshold.
In addition, we can calculate the effective number of ``yes'' and ``no'' votes.\footnote{Which one can think
of as the number of Heads and Tails in the aforementioned tutorial.}

@@

To continue with our example, let's say that $M_1$ and $M_3$ voted for a decision with $0.7$ and against with $0.4$,
respectively.
We are using range voting on $[-1, 1]$ range, so those votes are $v_1 = V_1 = 0.7$ and
$v_3 = V_3 = -0.4$.
